### 2019-03-25 README.Rmd
Update README.Rmd

# master.paper

@@

Or you can install this compendium as an R package, master.paper, from GitHub with:
```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("LiYingWang/master.paper")
```
### Licenses

>>>>

# kwlornaments

@@

Or you can install this compendium as an R package, master.paper, from GitHub with:
```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("LiYingWang/kwlornaments")
```
### Licenses
